Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-06-16 manuscript.Rmd
made the table

>>>>

### Sensor Configuration
<!-- data/reduce, duplicates of the group_split metrics but performed on reductions of sensor features from group_split_sensor_reduce.R -->

```{r metrics-reduce, cache=TRUE, cache.extra=tools::md5sum("data/group_split_metrics.csv")}
all_files = list.files("data/reduce", full.names = T, pattern = ".csv")
overall_files = all_files %>% discard(str_detect(., pattern = "class"))
sensor_comp <- read_csv(overall_files, id = "type")
sensor_comp <- sensor_comp %>% mutate(type = str_remove(type, "data/reduce/reduce_metrics_"),
                              type = str_remove(type, ".csv"),
                              type = factor(type,
                              levels = c("all", "left_side", "right_side", "hips", "ankles",
                                         "left_hip","left_ankle", "right_hip", "right_ankle"),
                              labels = c("All", "Left Hip/Ankle", "Right Hip/Ankle", "Both Hips", "Both Ankles", 
                                         "Left Hip", "Left Ankle", "Right Hip", "Right Ankle")),
                              Model = factor(model, levels = c("group", "split", labels = c("Group", "Individual"))))

metrics_sensor <- sensor_comp %>% group_by(Model, type) %>% 
  get_summary_stats(`Overall Accuracy`) %>% 
  select(-(variable:max), -(q1:mad), -se, -ci) %>% 
  pivot_wider(names_from = Model, values_from = c("median", "mean", "sd")) %>% 
  relocate(mean_group, .after = median_group) %>% 
  relocate(sd_group, .after = mean_group) %>% 
  mutate(across(-type, ~ apa_num(.x, digits = 3)))

apa_table(metrics_sensor, col.names = c("Sensors", "Median", "Mean", "SD", "Median", "Mean", "SD"),    col_spanners = list("Group" = c(2, 4), "Individual" = c(5, 7)), midrules = c(1,5),
          caption = "Median, mean, and SD of overall accuracy calculated with different sets of sensor features. The top row shows performance using all features calculated from the four sensors. Rows 2-5 show accuracy using pairs of sensors (left hip and ankle, right hip and ankle, left and right hip, left and right ankle), and rows 6-9 show accuracy using each individual sensor.")
```

### 2023-06-16 manuscript.tex
made the table

>>>>

\hypertarget{sensor-configuration}{%
\subsubsection{Sensor Configuration}\label{sensor-configuration}}

\caption{\label{tab:metrics-reduce}Median, mean, and SD of overall accuracy calculated with different sets of sensor features. The top row shows performance using all features calculated from the four sensors. Rows 2-5 show accuracy using pairs of sensors (left hip and ankle, right hip and ankle, left and right hip, left and right ankle), and rows 6-9 show accuracy using each individual sensor.}

\begin{tabular}{lllllll}
\toprule
 & \multicolumn{3}{c}{Group} & \multicolumn{3}{c}{Individual} \\
\cmidrule(r){2-4} \cmidrule(r){5-7}
Sensors & Median & Mean & SD & Median & Mean & SD\\
\midrule
All & 0.894 & 0.846 & 0.131 & 0.933 & 0.916 & 0.072\\ \midrule
Left Hip/Ankle & 0.891 & 0.824 & 0.177 & 0.915 & 0.901 & 0.071\\
Right Hip/Ankle & 0.842 & 0.800 & 0.167 & 0.897 & 0.898 & 0.086\\
Both Hips & 0.859 & 0.791 & 0.195 & 0.907 & 0.898 & 0.072\\
Both Ankles & 0.797 & 0.719 & 0.196 & 0.864 & 0.844 & 0.108\\ \midrule
Left Hip & 0.842 & 0.762 & 0.208 & 0.889 & 0.872 & 0.077\\
Left Ankle & 0.717 & 0.667 & 0.208 & 0.851 & 0.825 & 0.117\\
Right Hip & 0.846 & 0.772 & 0.178 & 0.896 & 0.876 & 0.092\\
Right Ankle & 0.704 & 0.683 & 0.160 & 0.830 & 0.819 & 0.114\\
\bottomrule
\end{tabular}
